\documentclass[10pt]{extarticle}
%\documentclass[]{file}
\usepackage[margin=0.2in]{geometry}
\usepackage{romannum}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
%name and details
\begin{document}
\begin{flushleft}
\noindent {\huge\textbf{Priyanka Soni}}
\end{flushleft}
\href{mailto:priyankasoni01999@gmail.com}{\color{black}{\raisebox{-0.2\height}\faEnvelope\ priyankasoni01999@gmail.com}} \hfill Find Me:
 \\
 \small \raisebox{-0.1\height}\faPhone\ +91-7320972030 \hfill
\href{https://www.linkedin.com/in/priyanka-soni-131668176} {\large \raisebox{-0.2\height}\faLinkedin} \href{https://github.com/PSoni8}{\large \raisebox{-0.2\height}\faGithub}
\vspace{-4pt}
\\
\noindent\rule[0.5ex]{\linewidth}{1pt}
%education
{\large \textbf{\begin{tcolorbox}\textsc{Education}\end{tcolorbox}}}
\begin{center}
\begin{tabular}{|p{2.0cm}|p{7.5cm}|p{8cm}|p{1.3cm}|}
\hline
\centering{\textbf{Year}} & \centering{\textbf{Degree/Certificate}} & \centering{\textbf{Institute}} & \textbf{CPI/$\%$}\\
\hline
\centering{2018 - 2022} & \centering{B.Tech in Electronics \& Communication Engineering} & \centering{MN National Institute of Technology Allahabad, India} & 8.11/10\\
\hline
\centering{2017} & \centering{CBSE(\Romannum{12})} & \centering{DAV Public School, Sector-4, Bokaro Steel City} & 94$\%$\\
\hline
\centering{2015} & \centering{CBSE(\Romannum{10})} & \centering{BISSS 8/B, Sector-8, Bokaro Steel City} & 9.4/10\\
\hline
\end{tabular}
\end{center}
%experience
{\large \textbf{\begin{tcolorbox}\textsc{Internships}\end{tcolorbox}}}
\begin{itemize}
\item \href{https://www.linkedin.com/company/siemens/mycompany/verification/}{\textbf{Siemens India}}\hfill\hfill(\textit{June,2020-Present})\\
\textbf{Summer Intern}\hfill\hfill\textit{Goa, India}
     \begin{itemize}
         \item \underline{\textbf{Project Idea}} : Linear Drive Greasing Automation
         \item After manufacture of Shaft in industries, manual Greasing takes time.
         \item We are working on \textbf{automation} model for \textbf{greasing of shafts} in minimum time \& minimum cost.
     \end{itemize}
\item \href{https://www.linkedin.com/company/fifo-solutions/}{\textbf{Fifo Solutions}}\hfill\hfill(\textit{April,2021-Present})\\
\textbf{Web Development Intern}\hfill\hfill\textit{Andhra Pradesh, India}
    \begin{itemize}
        \item Fifo Solutions is a \textbf{startup} which also provides IT solutions.
        \item Working in technology team as a Web Developer on \textbf{Frontend} and \textbf{Databases}.
        \item Worked on \textbf{frontend of 3 client projects} and Built \textbf{user-friendly and responsive UI} for all.
        \item Built responsive and attractive \textbf{Navbar, footer, forms, content} etc..
        \item Built \textbf{POST API} to store form data.
        \item \underline{\textbf{Tech Stacks}} - HTML, CSS, BootStrap, Javascript, Nodejs, Expressjs, MongoDB
    \end{itemize}
\item \href{https://www.linkedin.com/company/siemens/mycompany/verification/}{\textbf{Siemens India}}\hfill\hfill(\textit{June,2020-Sep,2020})\\
\textbf{Summer Project Intern}\hfill\hfill\textit{Mumbai, India}
      \begin{itemize}
          \item \underline{\textbf{Project Idea}} : \href{https://github.com/PSoni8/Seimens-Project}{\textbf{Automation in Hospital Systems}}
          \item It is solution for Hospitals in which we tried \textbf{to minimize human contact} to avoid the spread of COVID-19 virus.
          \item We also tried \textbf{to minimize the cost} (approx. 6500-7000 rupees) so that small hospitals can also work on this solution.
          \item We used \textbf{Automation} using Sensors and Microcontrollers (Arduino, 20 pin AT89C2051).
          \item We also built \textbf{Web Application} for Online Appointment \& \textbf{OCR} for Offline Registration.
          \item \underline{\textbf{Tech Stacks}} -  HTML, CSS, Javascript, SQL, Php, Python, OpenCV, C/C++
      \end{itemize}
\end{itemize}
\vspace{2mm}
%Projects
{\large \textbf{\begin{tcolorbox}\textsc{Projects}\end{tcolorbox}}}
\begin{itemize}
\item \href{https://github.com/PSoni8/Bookcentre}{\textbf{Book Centre}}
        \begin{itemize}
           \item An \textbf{Online platform} for retailers and customers to \textbf{sell and buy books} respectively.
           \item Having features like \textbf{Role based access} and \textbf{email alert} for admin and users, \textbf{Cart and Online Payments}, Supply-Chain Management, etc..
           \item \textbf{Tech Stack/Area} - Web development, Reactjs, Bootstrap, Nodejs, Expressjs and MongoDB.
        \end{itemize}
\item \href{https://github.com/PSoni8/Find-my-Caption}{\textbf{Find my Caption}}
         \begin{itemize}
             \item A model which \textbf{predicts caption} for the \textbf{provided image} by users.
             \item It is using \textbf{CNN and LSTM} deep learning models.
             \item It’s trained using \textbf{Flickr-8k dataset} and \textbf{VGG16 model}.
             \item \textbf{Tech Stack/Area} - Machine Learning, Python, Keras
         \end{itemize}
\end{itemize}
\vspace{2mm}
%skills
{\large \textbf{\begin{tcolorbox}\textsc{Technical Skills}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Programming: }C, C++, Data Structures, Algorithms
\item \textbf{Framework/Language: }Python/Machine Learning, JavaScript, HTML, CSS, Bootstrap, React, Material-UI, Node, Express
\item \textbf{Database: }MySQL, MongoDB
\item \textbf{Tool: }Git/Github, Postman, VS Code, LaTeX, Kaggle, Google collab
\end{itemize}
\vspace{2mm}
%achievements
{\large \textbf{\begin{tcolorbox}\textsc{Achievements}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Academic Achievements}
    \begin{itemize}
       \item Selected as Participant in \href{https://www.linkedin.com/posts/priyanka-soni-131668176_opensource-github-gssoc2021-activity-6768059710504628224-zK4j/}{\color{black}\textbf{GirlScript Summer of Code}} - 2021.
           \begin{itemize}
               \item It is 3 month Open-Source Program by GirlScript like GSoC.
               \item I have Contributed on 3 repositories.
           \end{itemize}
        \item Appreciation from \href{https://www.linkedin.com/posts/priyanka-soni-131668176_ideapresentationcontest-iot-innovation-activity-6743422132929343488-fRUb/}{\color{black}\textbf{Synopsys}} for ”Inno Champ Contest” - 2020.
          \begin{itemize}
              \item It is Idea-Presentation Program Organised by Synopsys.
              \item I have Proposed a model on "To create Cleaner and Healthier Planet".
          \end{itemize}
       \item Scored more than 75\% in \href{https://drive.google.com/file/d/1FfOOm94LawOPaGOGxPQHwiO4TyZkc5h6/view}{\color{black}\textbf{NQT}} - 2020.
         \begin{itemize}
           \item It is 3 hours test of Numerical, Verbal and Reasoning Ability conducted by TCS.
         \end{itemize}
       \item Scholarship for 4 Years By \href{https://drive.google.com/file/d/1XFUYs_kH-7Q7BmaebOLJVNOLyD0d4iTg/view}{\color{black}\textbf{Siemens India}} - 2018.
          \begin{itemize}
            \item Mechatronics training \& Career Counselling by Siemens.
            \item Soft Skill Training by Growth Centre, RIPE Global \& Smile Foundation.
            \item Tuition fees of 4 years and annual allowances.
          \end{itemize}
      \item Scored 16293 AIR in \href{https://drive.google.com/file/d/1ybuqeNcAqsaaAtMSv_K6zBx6bJwiuTa0/view}{\color{black}\textbf{JEE-Mains}} over 11 lakhs aspirants - 2018.
      \item Scored 320 out of 450 in \textbf{BITSAT} - 2018.
      \item 2nd Rank in School, \textbf{Scored 100\%} in Painting \&  \href{https://drive.google.com/file/d/1GiHNUBNS30WbXInxHmCdSKwQ_ot4lDs5/view}{\color{black}\textbf{Excellence Award by Jagran}} in AISSCE- 2017.
      \item \href{https://drive.google.com/file/d/1GhwFc3VOeL1bHnBPuYxt3zKOOEPqwbSr/view}{\color{black}\textbf{Academics Excellence Award}} in 11th standard - 2016.
      \item 2nd Rank in School in AISSE - 2015.
    \end{itemize}
\item \textbf{Programming Achievements}
     \begin{itemize}
        \item 3 stars, 5 stars \& 4 stars in DSA, C++ \& C respectively on \href{https://www.hackerrank.com/priyankasoni0191}{\textbf{HackerRank}}.
         \item Feb. Starters’21-Global Rank : 4400 \& April Starters’21-Global Rank : 3567 on \href{https://www.codechef.com/users/priyanka_1507}{\textbf{CodeChef}}.(Rating : 1459)
         \item DSA Contest Rank : 142 \& Feb Easy’21 Rank : 262 on \href{http://www.hackerearth.com/@priyanka2228}{\textbf{HackerEarth}}.(Rating : 1285)
         \item \href{https://codeforces.com/profile/PS1507}{\textbf{CodeForces}}.(Rating : 820) \& \href{https://leetcode.com/priyanka_1507/}{\textbf{LeetCode}}.
          \item Kick Start’21 Round-B \href{https://drive.google.com/file/d/1LsFgjid-EoDQHQq91LWicyegafVAtmCc/view?usp=sharing}{\textbf{Rank}}  : 5632 \& Women CodeJam I/O \href{https://drive.google.com/file/d/1LsDfhp0fyK9fyNiSBHvNpPuZ4PJZGUOA/view?usp=sharing}{\textbf{Rank}} : 4065 of \textbf{Google Coding Competitions}.
     \end{itemize}
\end{itemize}
\vspace{2mm}
%extra-curricular
{\large \textbf{\begin{tcolorbox}\textsc{Extra-Curricular Activities}\end{tcolorbox}}}
\begin{itemize}
\item \textbf{Sports}
  \begin{itemize}
    \item \textbf{Gold Medal} in Volleyball on College Sports Day(Josh) - 2019.
  \end{itemize}
\item \textbf{Position of Responsibility}
  \begin{itemize}
    \item \textbf{Mentor of Electronics Society} of MNNIT for guiding juniors in Web Development - May’2021-present.
    \item Head Girl and House Caption for 2 years in DAV Public School - 2015 - 2017.
    \item House Caption (Rajendra house) for 2 years in BISSS 8/B - 2013 - 2015.
  \end{itemize}
\end{itemize}
\end{document}
